ICBEdataset figure Metro Maps

### 2022-07-17 replication_paper/rmd/CrisisMaps.Rmd
v1.1

---
title: "Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises"

#https://bookdown.org/yihui/bookdown/a-single-document.html
#https://stackoverflow.com/questions/52531637/knitr-rmarkdown-latex-how-to-cross-reference-figures-and-tables-in-2-different/52532269#52532269
#https://stackoverflow.com/questions/51595939/bookdown-cross-reference-figure-in-another-file
#https://stackoverflow.com/questions/25824795/how-to-combine-two-rmarkdown-rmd-files-into-a-single-output/51521542#51521542
output: 
  bookdown::pdf_book:
    toc: yes
    latex_engine: xelatex

bibliography: ICBintro.bib

#Disabled several the caused errors
header-includes:
# - \usepackage{xr} \externaldocument{appendix} #External references from the appendix
# - \usepackage{tinytex}
  - \usepackage[utf8]{inputenc}
  - \usepackage{pifont}
  - \usepackage{newunicodechar}
  - \newunicodechar{✓}{\ding{51}}
  - \newunicodechar{✗}{\ding{55}}
  - \usepackage{array}
  - \usepackage{ctable} # added for demo
  - \usepackage{natbib} #added for latex citation within huxtable
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{titlesec}
#  - \usepackage[parfill]{parskip}
  - \usepackage{makecell}
  - \usepackage{graphicx}
  - \usepackage{caption}
#  - \usepackage[capposition=top]{floatrow}
  - \titleformat{\subsubsection}{\normalfont\normalsize\itshape}{\thesubsubsection}{1em}{}
  - \titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{0ex plus .2ex}
#  - \DeclareUnicodeCharacter{00A0}{ }
  - \usepackage{setspace}
  - \usepackage{cellspace}
  - \setlength\cellspacetoplimit{0.8ex}
  - \renewcommand{\arraystretch}{0.8}
  - \AtBeginEnvironment{tabular}{\singlespacing}
  - \AtBeginEnvironment{lltable}{\singlespacing}
#  - \usepackage[ruled,vlined,linesnumbered]{algorithm2e}
  - \usepackage{subcaption}
  - \usepackage{atbegshi}% http://ctan.org/pkg/atbegshi
  - \usepackage{float}
#  - \usepackage{eso-pic,graphicx,transparent}
#  - \usepackage[perpage]{footmisc}
  - \usepackage{algorithm}
  - \usepackage[algo2e]{algorithm2e}
  - \usepackage{amsmath}
  - \usepackage{afterpage}
  - \usepackage{placeins}
  - \usepackage{rotating, float, caption}
#https://tex.stackexchange.com/questions/131646/algorithm2e-command-algorithm-already-defined

---

```{r library loads, eval=T, echo=F, cache=F, results='hide', message=F}

flag_folder_small="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_data/in/flags_small/"

knitr::opts_chunk$set(echo = F, echo=F, cache=F, results='hide', message=F, warning=F) #Global options

#library(pacman)
library(googlesheets4)
library(tidyverse)
library(janitor)
library(flextable)
library(ggplot2)
library(cowplot)
library(ggtext)
#set_flextable_defaults(fonts_ignore=TRUE) #Warning: fonts used in `flextable` are ignored because the `pdflatex` engine is used and not `xelatex` or `lualatex`. You can avoid this warning by using the `set_flextable_defaults(fonts_ignore=TRUE)` command or use a compatible engine by defining `latex_engine: xelatex` in the YAML header of the R Markdown document.
library(ftExtra)
options(tidyverse.quiet = TRUE)
options(gargle_oauth_email = TRUE)

#install.packages('stargazer')
#install.packages('kableExtra')
#! sh: 1: pdflatex: not found
#sudo apt-get install texlive-latex-recommended texlive-fonts-recommended

#! LaTeX Error: File `letltxmacro.sty' not found.
#sudo apt-get install texlive-latex-extra

library(pacman)
library(igraph)
library(tidyverse)
library(flextable)
library(ftExtra)

```{r data loads, eval=T, echo=F, cache=F, results='hide', message=F}

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds"))
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds") )

ICBe_events_agreed <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
dim(ICBe_events_agreed)

icb_events_long <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
dim(icb_events_long)

ICBe_crises_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.Rds"))

ICBe_events_agreed_markdown <- readRDS( paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds"))

#oh is it because break is reserved in R? lol
#icb_crises <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb1v14.csv")) %>% janitor::clean_names()
icb_crises  <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) %>% janitor::clean_names()
icb_crises$start_simple <- icb_crises$yrtrig+(icb_crises$motrig/12)
icb_crises$end_simple <- icb_crises$yrterm+(icb_crises$moterm/12)

#somehow break of all things is a b roken name
#icb_actors <- read_csv(file=paste0(here::here(), "/data_other_datasets/icb/icb2v14.csv"))
icb_actors <- read.csv(paste0(here::here(), "/replication_data/in/icb2v14.csv"))

# Appendix A Corpus and Cases
\hphantom{em}
## Table A1: ICBe Crises and Summary Information {#app:crises}
\hphantom{em}

```{r ICBe Crisis Summaries, eval=T, echo=F, results='hide', include=T, message=F, cache=F, warning=F}

#The answer is I have to include it as an image, none of the table options were compiling correctly without error
#,  ft.arraystretch=0.75

temp_all <-  ICBe_crises_markdown %>% ungroup() %>% dplyr::select(
                    crisno, crisis_text,  yrtrig , yrterm,  n_sentence_number_int_aligned, n_events, 
                    coders_expert , 
                    coders_novice ,
                    actors , 
                    units_domains, 
                    forces_fatalities
                    ) %>%
              mutate_all(as.character) %>%
              mutate(crisis_text = crisis_text %>% stringr::str_to_title() %>% str_replace("Ii$","II"))

convert_to_ft <- function(x){
     x %>% flextable::as_flextable() %>%
      flextable::set_header_labels(values =
          list(crisno = "#",
                crisis_text = "Title",
                yrtrig = "Start",
                yrterm = "End",
                n_sentence_number_int_aligned = "Sent.",
                n_events = "Events",
                coders_expert = "Exp.",
                coders_novice = "Nov.",
                actors = "Actors",
                units_domains = "Units/Domains",
                forces_fatalities = "Forces/Fatalities"
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::add_header(values =
          list(crisno = "Crisis",
                crisis_text = "Crisis",
                yrtrig = "Years",
                yrterm = "Years",
                n_sentence_number_int_aligned = "Counts",
                n_events = "Counts",
                coders_expert = "Coders",
                coders_novice = "Coders"#,
                #value_markdown = "Abstract"
               ) ) %>%
      flextable::merge_h(part = "header" ) %>%
      flextable::width( j = 1, width=0.3)  %>%
      flextable::width( j = 2, width=2.75)  %>%
      flextable::width( j = 3, width=0.6)  %>%
      flextable::width( j = 4, width=0.6)  %>%
      flextable::width( j = 5, width=0.25)  %>%
      flextable::width( j = 6, width=0.25)  %>%
      flextable::width( j = 7, width=0.25)  %>%
      flextable::width( j = 8, width=0.35)  %>%
      flextable::width( j = 9, width=2.5)  %>%
      flextable::width( j = 10, width=1.5)  %>%
      flextable::width( j = 11, width=1.0)  %>%
      flextable::fontsize(size = 9, part = "all") %>%
      flextable::padding(padding = 0.1, part = "all") %>%
      flextable::line_spacing(space = 1, part = "body") %>%
      flextable::bg( i = which( 1:nrow(x) %% 2 == 1)  , part = "body", bg = "#EFEFEF") %>%
      ftExtra::colformat_md(j = 9:11, part="body")
}

temp_all %>% ungroup() %>% filter(crisno %in% c(1:60) )  %>% convert_to_ft() %>%
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(61:120) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(121:180) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(181:240) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(241:300) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(301:360) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(361:420) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png", zoom=1)

temp_all %>% ungroup() %>% filter(crisno %in% c(421:500) ) %>% convert_to_ft()  %>% 
  save_as_image(path="/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png", zoom=1)

\begin{figure}[H]
\caption{ICBe Crises Summary Statistics \label{fig:case_study_cuban_precision}}
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft1.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft2.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft3.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft4.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft5.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft6.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft7.png"}}
\end{figure}

\begin{figure}[H]
\centering{\includegraphics[ height=21cm]{"/mnt/8tb_a/rwd_github_private/ICBEdataset/replication_paper/pnas_draft/crisis_text_counts_ft8.png"}}
\end{figure}

## Table A2: Verb Meanings (Glosses) found in the ICB Corpus (top 200) {#app:verbs}
\hphantom{em}

```{r , echo=F, results='hide', message=F, warning=F, eval=T , cache=F}

#Switched to spans here
icb_text <- ICBe_events_agreed %>% dplyr::select(crisno,sentence_number_int_aligned, sentence=sentence_span_text) %>% distinct() %>% dplyr::mutate_at(vars(sentence_number_int_aligned), as.numeric) %>% arrange(crisno,sentence_number_int_aligned)

# writeLines(icb_text$sentence %>% na.omit() %>% iconv("UTF-8", "ASCII", "?"), paste0(here::here(), "/replication_data/temp/sentences.txt"), useBytes = T)

fromscratch=F
if(fromscratch){
  #Here we use spacy to extract verbs from the sentences
  p_load("spacyr")
  #spacy_install() 
  spacy_initialize(model = "en_core_web_sm")

  parsed <- spacy_parse(icb_text$sentence, nounphrase = TRUE)
  parsed_consolidated <- nounphrase_consolidate(parsed)
  parsed$doc_id_num <- parsed$doc_id %>% str_replace_all("text","") %>% as.numeric()
  parsed$crisno <- icb_text$crisno[parsed$doc_id_num]
  parsed$sentence_number_int_aligned <- icb_text$sentence_number_int_aligned[parsed$doc_id_num]  %>% as.numeric()
  parsed$sentence <- icb_text$sentence[parsed$doc_id_num]

  parsed %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))

  entities <- entity_extract(parsed, type = "all")
  entities %>% saveRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))

} else {
  parsed <- readRDS(paste0(here::here(), "/replication_paper/data/temp/parsed.Rds"))
  entities <- readRDS(paste0(here::here(), "/replication_paper/data/temp/entities.Rds"))

>>>>

---
title: "ICBEdataset figure Metro Maps"
output: html_document
---

# Metro Maps

```{r}
global_check_overlap=F
```

#devtools::install_github('davidgohel/ggiraph')
library(ggplot2)
library(ggiraph)

library(flextable)
library(ftExtra)
library(tidyverse)
library(googlesheets4)
library(RColorBrewer)
library(tidyverse)
library(ggraph)
#library(edgebundle)
library(igraph)
library(stringr)

rex_paste <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}
rex_count <- function(x) { x %>% unique() %>% na.omit() %>% sort() %>% paste0(sep=";", collapse=";")}

# Common Preprocessing and Loads

```{r echo=FALSE, include=FALSE, eval=T}

icb_events_long <- readRDS( paste0(here::here(), '/replication_data/out/ICBe_V1.1_events_agreed_long.Rds'))
icb_events <- readRDS(file=paste0(here::here(),'/replication_data/out/ICBe_V1.1_events_agreed.Rds'))

icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/icb1v14.csv")) 
#icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds") )

target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
dictionary_actors_labels    <- readxl::read_excel(target_file, sheet="actors") %>% 
                              dplyr::select(crisno, value_normalized=value_normalized_wikidata_id, value_normalized_label) %>% dplyr::distinct() %>% na.omit()

#Design specification
#Time flows downward
#Each actor gets a line
#Spacing between lines should be dynamic, to allow for readability between
#We want the name of each actor to be labeled at the start of their line
#Unilateral actions printed above

#dpr/lpr is broken
actor_translator <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", 
                                sheet="actor_translator") #%>% janitor::clean_names() 
#Convert to a local file for pushing
#actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator") #Ya we just add colors to the actor translator and we're good
pallet <- setdiff(c(brewer.pal(n=20, "Dark2"), brewer.pal(n=20, "Set1"), brewer.pal(n=20, "Paired")), c("#666666", "#999999", "#FFFF99","#FFFF33"))
actor_translator$actor_color = rep(pallet, length=nrow(actor_translator))

icb_crises$start_simple <- icb_crises$yrtrig+(icb_crises$motrig/12)
icb_crises$end_simple <- icb_crises$yrterm+(icb_crises$moterm/12)

# ICBe

## ICBe metro plots

#icb_events_pruned_labeled %>% dplyr::select(start_time)

icbe_metro_plots <- function(crisis=196, prune_rare=T){

  print(crisis)
  #crisis=471
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_metro_plot_", crisis, ".Rds")

  icb_events_subset <-  icb_events %>% 
                                 ungroup() %>%
                                 dplyr::filter(crisno==crisis) %>%  #417 196
                                 dplyr::filter(!is.na(think_actor_a) | !is.na(say_actor_a) | !is.na(do_actor_a))   %>%
                                 #dplyr::select(date) %>% #for date debugging
                                 #mutate(date_asdate=date %>% str_replace_all("th|end of|after",'') %>% trimws() %>% anytime::anydate(useR=F)) %>%
                                 #mutate(year = date %>% stringr::str_extract(pattern = "[0-9]{4}") %>% as.numeric() ) %>%
                                 #mutate(year = lubridate::year(date_asdate)) %>% #This should all be considered hacky approximations
                                 #mutate(year = ifelse(year<1900, NA, year)) %>%
                                 mutate(decade=date_earliest_decade %>% as.numeric() ) %>%
                                 mutate(year=date_earliest_year %>% as.numeric() ) %>%
                                 mutate(month= date_earliest_month %>% as.numeric() ) %>%
                                 mutate(day= date_earliest_day %>% as.numeric()  ) %>%
                                 arrange(desc(do_timing %in% 'long before crisis'), sentence_number_int_aligned) %>%
                                 tidyr::fill(decade, .direction="downup") %>%
                                 tidyr::fill(year, .direction="downup") %>%
                                 tidyr::fill(month, .direction="downup") %>%
                                 tidyr::fill(day, .direction="downup") %>% 
                                 mutate(point_in_time_year = year %>% as.numeric())  %>% 
                                 mutate(point_in_time_month = month %>% as.numeric()) %>% 
                                 arrange(decade, year,month,day) %>%
                                 mutate(sent= cumsum((sentence_number_int_aligned == lag(sentence_number_int_aligned) ) %in% FALSE) ) #this is now our new order

  icb_events_subset_diad <- icb_events_subset %>% 
                                     mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
                                     mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
                                     mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
                                     mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
                                     mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
                                     mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
                                                         interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
                                     mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
                                     mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
                                     mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
                                     mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
                                     filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
                                     dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
                                                    sent,
                                                    think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
                                                    thinkkind, sayintkind, dokind,
                                                    point_in_time_year, point_in_time_month
                                                    ) %>% distinct() %>%
                                filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind)))

  notes=NULL
  if(prune_rare==T){
    actor_sent_counts <- 
      bind_rows(
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=think_actor_a),
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_a),
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=say_actor_b),
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_a),
          icb_events_subset %>% dplyr::select(sent=sentence_number_int_aligned,actor=do_actor_b)
        ) %>% 
          na.omit() %>%
          mutate(actor = strsplit(as.character(actor), ";")) %>% unnest(actor) %>% distinct() %>% count(actor) %>% arrange(n %>% desc() )

      #New pruning rule, either singletons or actors with less than 10% of the max actor
      singleton_actors <- actor_sent_counts %>% mutate(share_of_max=n/max(n)) %>% filter(n==1 | share_of_max<=0.1) %>% pull(actor) 
      left_over_count <- nrow(actor_sent_counts) - length(singleton_actors)
      if(left_over_count<3){
        #Skip pruning if it leaves less than 3 actors
      } else {

        actor_map <- dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) 
        actor_singleton_labels <- actor_map$value_normalized_label
        names(actor_singleton_labels) <- actor_map$actor
        actor_singleton_labels <- actor_singleton_labels[singleton_actors]

        notes <- paste("Not shown: ", paste( singleton_actors %>% sort(), collapse="; " )) %>% stringi::stri_wrap(width=80) %>% paste(collapse="\n")

        #Easiest thing is to just prune the original data
        icb_events_subset <- icb_events_subset %>%
          filter(!(
                think_actor_a %in% singleton_actors | #This doesn't work for joint ones
                say_actor_a %in% singleton_actors |
                say_actor_b %in% singleton_actors |
                do_actor_a %in% singleton_actors |
                do_actor_b %in% singleton_actors 
          ) )

          #recreate diads again using the new sentence numbers
          icb_events_subset_diad <- icb_events_subset %>% 
                                             mutate(think_actor_a = strsplit(as.character(think_actor_a), ";")) %>% unnest(think_actor_a, keep_empty=T) %>%
                                             mutate(say_actor_a = strsplit(as.character(say_actor_a), ";")) %>% unnest(say_actor_a, keep_empty=T) %>%
                                             mutate(say_actor_b = strsplit(as.character(say_actor_b), ";")) %>% unnest(say_actor_b, keep_empty=T) %>%
                                             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a, keep_empty=T) %>%
                                             mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b, keep_empty=T) %>%
                                             mutate(dokind=paste(act_deescalate,act_escalate,act_uncooperative,act_cooperative, interact_deescalate,
                                                                 interact_escalate, interact_decreasecoop, interact_increasecoop, sep=";")) %>%
                                             mutate(thinkkind = strsplit(as.character(thinkkind), ";")) %>% unnest(thinkkind, keep_empty=T) %>%
                                             mutate(sayintkind = strsplit(as.character(sayintkind), ";")) %>% unnest(sayintkind, keep_empty=T) %>%
                                             mutate(dokind = strsplit(as.character(dokind), ";")) %>% unnest(dokind, keep_empty=T) %>%
                                             mutate(dokind=ifelse(dokind=='',NA,dokind)) %>%
                                             filter(!is.na(thinkkind) | !is.na(sayintkind) | !is.na(dokind)) %>%
                                             dplyr::select(sentence_number_int_aligned, #You have to keep this to remove dupe monads from the same sentence
                                                            sent,
                                                            think_actor_a,say_actor_a,say_actor_b,do_actor_a,do_actor_b,
                                                            thinkkind, sayintkind, dokind,
                                                            point_in_time_year, point_in_time_month
                                                            ) %>% distinct() %>%
                                        filter(!duplicated(paste(sent,think_actor_a, say_actor_a, say_actor_b, do_actor_a, do_actor_b, thinkkind, sayintkind, dokind))) %>%
                                        filter(!(
                                              think_actor_a %in% singleton_actors | #This doesn't work for joint ones
                                              say_actor_a %in% singleton_actors |
                                              say_actor_b %in% singleton_actors |
                                              do_actor_a %in% singleton_actors |
                                              do_actor_b %in% singleton_actors 
                                        ) ) %>% 
                                       arrange(sent) %>%
                                       mutate(sent= cumsum((sent == lag(sent) ) %in% FALSE) ) #
      }
  }

  #Order actors by how many interactions they have together
  temp <- bind_rows(
    icb_events_subset_diad  %>% 
      dplyr::select(say_actor_a, say_actor_b, sent) %>% na.omit()  %>% dplyr::rename(actor_1=say_actor_a, actor_2=say_actor_b),
    icb_events_subset_diad %>% 
      filter(is.na(sayintkind)) %>%  dplyr::select(do_actor_a, do_actor_b, sent) %>% na.omit() %>% dplyr::rename(actor_1=do_actor_a, actor_2=do_actor_b)
  )  %>% arrange(actor_1, actor_2) %>% distinct()

  #new plan is to minimize the number of crossovers
  temp2 <- bind_rows(
    temp,
    temp %>% setNames(c("actor_2", "actor_1", "sent"))
  ) %>% count(actor_1, actor_2) %>% arrange(actor_1, actor_2) %>% arrange(n) %>%
  rowwise() %>%
  mutate(actor_unordered= ifelse(actor_1>actor_2, paste(actor_1, actor_2),paste(actor_2, actor_1) ) ) %>%
  arrange(desc(n))

  temp2_wide <- temp2 %>% tidyr::pivot_wider(id_cols=c(actor_1), names_from=actor_2, values_from=n) %>% mutate_if(is.numeric, tidyr::replace_na, 0) %>% as.data.frame()
  rownames(temp2_wide) <- temp2_wide$actor_1
  temp2_wide$actor_1 <- NULL
  temp2_wide <- temp2_wide %>% as.matrix()
  temp2_wide <- 1 -   (temp2_wide/max(temp2_wide))
  temp2_wide <- temp2_wide[sort(rownames(temp2_wide)), sort(colnames(temp2_wide))]
  hc <- hclust(temp2_wide %>% as.dist(), method="single")
  diag(temp2_wide) <- 0
  temp2_wide_pca <- prcomp(temp2_wide, center = F,scale. = F, retx=F, rank=1) #just run PCA on the distance matrix and order along the first eigenvalue

  #ideal_ordering <- hc$labels[hc$order] #There's a bug here, put all the isolated nodes by themselves first
  ideal_ordering <- temp2_wide_pca$rotation %>% as.data.frame() %>% arrange(PC1) %>% rownames() #This all works but it's not optimizing what we want which is to minimize the number of cross over events

  #####Nodes
  icb_events_subset_nodes <- 
            bind_rows(
                      icb_events_subset_diad %>% dplyr::select(sent, actor=think_actor_a, point_in_time_year, point_in_time_month) ,
                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_a, point_in_time_year, point_in_time_month) ,
                      icb_events_subset_diad %>% dplyr::select(sent, actor=say_actor_b, point_in_time_year, point_in_time_month) ,
                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_a, point_in_time_year, point_in_time_month) ,
                      icb_events_subset_diad %>% dplyr::select(sent, actor=do_actor_b, point_in_time_year, point_in_time_month) 
            )  %>%
            filter(!is.na(actor)) %>%
           distinct()  %>% arrange(actor,sent) %>% mutate(actor_sent= actor %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>% #don't na omit this one
            mutate(x=actor %>% factor(levels=actor %>% unique() %>% setdiff(ideal_ordering) %>% c(ideal_ordering)) %>% as.numeric() *100 ,
                   y=sent*-1 *100)

  icbe_actor_to_qcode <- icb_events_long %>%
                         dplyr::filter(crisno==crisis  ) %>% 
                         filter(varname_normalized %>% str_detect("actor")) %>% 
                         dplyr::select(value_normalized,value_qcode) %>% 
                         na.omit() %>% distinct()

  date_sineposts <- icb_events_subset_nodes  %>%
                      mutate(x=max(x)+50) %>%
                      dplyr::select(sent, point_in_time_year, point_in_time_month,x,y) %>%
                      na.omit() %>% 
                      distinct() %>%  
                      mutate(sent=as.numeric(sent)) %>% arrange(sent) %>%
                      mutate(year_float=point_in_time_year+(point_in_time_month/12)) %>%
                      group_by(sent) %>%
                       filter(year_float==min(year_float)) %>%
                      ungroup() %>% as.data.frame() %>%
                      filter( row_number()==1 |  ( year_float > lag(year_float)  ) )  %>%
                      filter(!duplicated(year_float ) ) %>%
                      mutate(label=paste0(point_in_time_year,"-",month.abb[point_in_time_month]))

  # #Units
  # units <-   icb_events_subset %>% dplyr::select(sent, do_actor_a, interact_units) %>% na.omit()  %>% 
  #             mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
  #             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
  #             mutate(IMAGE=paste0(here::here(), '/replication_paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
  #             mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
  #             left_join(icb_events_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
  #             dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
  #             arrange(actor_sent, interact_units) %>%
  #             group_by(actor_sent) %>%
  #               mutate(units_count=n()) %>%
  #               mutate(middle=units_count/2) %>%
  #               mutate(units_number=row_number()) %>%
  #               mutate(offeset=(middle-units_number)*10)  
  #   
  # fatalities <-   icb_events_subset %>% 
  #                 dplyr::select(crisno, sent, do_actor_b, interact_fatalities) %>% na.omit() %>% #filter(interact_fatalities!='none') %>%
  #                 mutate(interact_fatalities = strsplit(as.character(interact_fatalities), ";")) %>% unnest(interact_fatalities) %>%
  #                 mutate(do_actor_b = strsplit(as.character(do_actor_b), ";")) %>% unnest(do_actor_b) %>%
  #                 mutate(actor_sent= do_actor_b %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
  #                 left_join(icb_events_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
  #                 rename(actor=do_actor_b) %>%
  #                 #dplyr::select(-sent, -do_actor_b) %>%
  #                 distinct() %>% 
  #                 mutate(interact_fatalities=interact_fatalities %>% 
  #                          factor(levels=c('none','individuals','tens','hundreds','thousands','tens of thousands','hundreds of thousands')) %>% as.numeric() ) %>%
  #                 arrange(actor_sent, interact_fatalities) %>%
  #                 group_by(actor_sent) %>%
  #                   filter(interact_fatalities==max(interact_fatalities, na.rm=T)) %>%
  #                 ungroup()
  #   
  # 
  # #table(icb_events$interact_fatalities)
  # #table(icb_events$interact_domains)
  # #table(icb_events$interact_forces)
  # 
  # 
  # units <-   icb_events_subset %>% 
  #             dplyr::select(sent, do_actor_a, interact_units) %>% na.omit()  %>% 
  #             mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
  #             mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
  #             mutate(IMAGE=paste0(here::here(), "/replication_paper/figures/metro_plots/symbols/",interact_units,'.png')) %>%
  #             mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
  #             left_join(icb_events_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
  #             dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
  #             arrange(actor_sent, interact_units) %>%
  #             group_by(actor_sent) %>%
  #               mutate(units_count=n()) %>%
  #               mutate(middle=units_count/2) %>%
  #               mutate(units_number=row_number()) %>%
  #               mutate(offeset=(middle-units_number)*5)

  ####Actor levels
  icb_events_subset_nodes_min <- 
    icb_events_subset_nodes %>% group_by(actor) %>% filter(sent==sent %>% min()) %>% ungroup() %>%
    left_join(dictionary_actors_labels %>% filter(crisno==crisis) %>% distinct() %>% rename(actor=value_normalized) ) %>%
    #rename(qcode=actor, actor=value_normalized_label) %>% #we used to normalize to qcode and n
    rowwise() #%>%
    #mutate(actor=actor %>% stringi::stri_wrap(width=15) %>% paste0(collapse='\n')) #do at plot time so I don't break colors

  g <- g %>% 
       add_edges(icb_events_subset_nodes_edges_time[,c('actor_sent','actor_sent_2')] %>% as.matrix() %>% t() %>% as.vector(),
                 actor=icb_events_subset_nodes_edges_time$actor, timeedge=T, leaf='', eventedge=F, bundle_count=1)
